A Gaussian process model of human electrocorticographic data

### 2018-10-11 paper/main.tex
another pass through main.tex [WIP]

\title{Towards human SuperEEG} 
\author{
  Lucy L. W. Owen$^{1}$,
  Andrew C. Heusser$^{1, 2}$, and
  Jeremy R. Manning$^{1\ast}$\\\\
$^{1}$Department of Psychological and Brain Sciences, Dartmouth College,\\
Hanover, NH 03755, USA\\
$^{2}$Akili Interactive,\\
Boston, MA 02110, USA}

@@

\begin{abstract}
  Human \textit{SuperEEG}\footnote{The term ``SuperEEG'' was coined by
    Robert J. Sawyer in his popular science fiction novel \textit{The
      Terminal Experiment}~\cite{Sawy95}} entails measuring ongoing
  neural activity throughout the entire living brain with perfect
  precision and arbitrarily high spatiotemporal resolution.  Although
  true SuperEEG is impossible using existing methods, here we present
  a model-based method for \textit{inferring} full-brain neural
  activity at millimeter-scale spatial resolutions and
  millisecond-scale temporal resolutions using standard human
  intracranial recordings.  Our approach assumes that different
  people's brains exhibit similar spatial correlations, and that
  activity and correlation patterns are spatially smooth.  One can
  then ask, for an arbitrary individual's brain: given recordings from
  a limited set of locations in that individual's brain, along with
  the observed spatial correlations learned from other people's
  recordings, how much can be inferred about ongoing activity at
  \textit{other} locations in that
  individual's brain?\\\\
  \footnotesize{\textbf{Keywords: Electrocorticography (ECoG),
      intracranial electroencephalography (iEEG), local field
      potential (LFP), epilepsy, maximum likelihood estimation,
      Gaussian process regression}}
\end{abstract}

@@

The current ``gold standard'' for precisely localizing signals and
sampling at high temporal resolution is to take (ECoG or iEEG)
recordings from implanted electrodes (but from a limited set of
locations in any given brain).  This begs the following question: what
can we infer about the activity exhibited by the rest of a person's
brain, given what we learn from the limited intracranial recordings we
have from their brain and additional recordings taken from
\textit{other} people's brains?  Here we develop an approach, which we
call \textit{SuperEEG}, based on Gaussian process
regression~\cite{Rasm06}.  SuperEEG entails using data from multiple
people to estimate activity patterns at arbitrary locations in each
person's brain (i.e., independent of their electrode placements).  We
test our SuperEEG approach using two large datasets of intracranial
recordings~\cite{SedeEtal03, SedeEtal07a, SedeEtal07b, MannEtal11,
  MannEtal12, EzzyEtal17, HoraEtal17, KragEtal17, KuceEtal17,
  LinEtal17, SoloEtal18, WeidEtal18, EzzyEtal18, KuceEtal18}.  We show
that the SuperEEG algorithm recovers signals well from electrodes that
were held out of the training dataset.  We also examine the factors
that influence how accurately activity may be estimated (recovered),
which may have implications for electrode design and
placement in neurosurgical applications.

>>>>

\title{A Gaussian process model of human electrocorticographic data} 
\author{
  Lucy L. W. Owen$^{1}$,
  Andrew C. Heusser$^{1, 2}$, and
  Jeremy R. Manning$^{1\ast}$\\\\
$^{1}$Department of Psychological and Brain Sciences, Dartmouth College,\\
Hanover, NH 03755, USA\\
$^{2}$Akili Interactive,\\
Boston, MA 02110, USA}

@@

\begin{abstract}
  We present a model-based method for inferring full-brain neural
  activity at millimeter-scale spatial resolutions and
  millisecond-scale temporal resolutions using standard human
  intracranial recordings.  Our approach assumes that different
  people's brains exhibit similar spatial correlations, and that
  activity and correlation patterns are spatially smooth.  One can
  then ask, for an arbitrary individual's brain: given recordings from
  a limited set of locations in that individual's brain, along with
  the observed spatial correlations learned from other people's
  recordings, how much can be inferred about ongoing activity at
  \textit{other} locations throughout that
  individual's brain?  We show that our approach generalizes across
  people and tasks, thereby providing a person- and task-general means
  of inferring high spatiotemporal resolution full-brain neural
  dynamics from standard low-density intracranial recordings.
  \\\\
  \footnotesize{\textbf{Keywords: Electrocorticography (ECoG),
      intracranial electroencephalography (iEEG), local field
      potential (LFP), epilepsy, maximum likelihood estimation,
      Gaussian process regression}}
\end{abstract}

@@

The current ``gold standard'' for precisely localizing signals and
sampling at high temporal resolution is to take (ECoG or iEEG)
recordings from implanted electrodes (but from a limited set of
locations in any given brain).  This begs the following question: what
can we infer about the activity exhibited by the rest of a person's
brain, given what we learn from the limited intracranial recordings we
have from their brain and additional recordings taken from
\textit{other} people's brains?  Here we develop an approach, which we
call \textit{SuperEEG}\textit{SuperEEG}\footnote{The term ``SuperEEG''
  was coined by Robert J. Sawyer in his popular science fiction novel
  \textit{The Terminal Experiment}~\cite{Sawy95}.  SuperEEG is a
  fictional technology that measures ongoing neural activity
  throughout the entire living human brain with perfect precision and
  at arbitrarily high spatiotemporal resolution.}, based on Gaussian
process regression~\cite{Rasm06}.  SuperEEG entails using data from
multiple people to estimate activity patterns at arbitrary locations
in each person's brain (i.e., independent of their electrode
placements).  We test our SuperEEG approach using two large datasets
of intracranial recordings~\cite{SedeEtal03, SedeEtal07a, SedeEtal07b,
  MannEtal11, MannEtal12, EzzyEtal17, HoraEtal17, KragEtal17,
  KuceEtal17, LinEtal17, SoloEtal18, WeidEtal18, EzzyEtal18,
  KuceEtal18}.  We show that the SuperEEG algorithm recovers signals
well from electrodes that were held out of the training dataset.  We
also examine the factors that influence how accurately activity may be
estimated (recovered), which may have implications for electrode
design and placement in neurosurgical applications.
